\documentclass[bachelor,xecjk]{cqu}  %单面打印版本
\usepackage{etex}
\def\tightlist{}

%%在这增加你需要的其它包
\definecolor{hellgelb}{rgb}{1,1,0.8}
\definecolor{colKeys}{rgb}{0,0,1}
\definecolor{colIdentifier}{rgb}{0,0,0}
\definecolor{colComments}{rgb}{1,0,0}
\definecolor{colString}{rgb}{0,0.5,0}
\usepackage{listings}
\lstset{%
    float=hbp,%
    basicstyle=\ttfamily\small, %
    identifierstyle=\color{colIdentifier}, %
    keywordstyle=\color{colKeys}, %
    stringstyle=\color{colString}, %
    commentstyle=\color{colComments}, %
    columns=flexible, %
    tabsize=4, %
    frame=single, %
    extendedchars=true, %
    showspaces=false, %
    showstringspaces=false, %
    numbers=left, %
    numberstyle=\tiny, %
    breaklines=true, %
   backgroundcolor=\color{hellgelb}, %
    breakautoindent=true, %
    captionpos=b,%
	xleftmargin=0pt%
}

\begin{document}

%-----------------------------------论文题目-------------------------------------------------
\xuehao{20121892}
\cntitle{基于深度学习的自增长图片验证码算法研究与实现}
\cnauthor{张乐}
\cnmajor{软件工程}
\cnteacher{葛永新}
\cnxueyuan{软件学院}
\entitle{Design and Implementation of automatic Increased Image-based CAPTCHA Algorithm using Deep Learning}
\enauthor{Le Zhang}
\enmajor{Software Engineering}
\enteacher{Prof. Yongxin Ge}
\enxueyuan{College of Software}
\cnkind{****}
\enkind{****}
%\cnzlteacher{ }  %%助理教师，如果必要，还要将cqu.cls中的有关该项前的%号去掉
%\enzlteacher{ }
\cndate{二O一六年六月}
\endate{June 2016}
%%%%只需修改上面的相关信息%%%%%%%%
\makecntitle 
\makeentitle 
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{Roman}

%------------------------------------文章摘要------------------------------------------------------------
\cnkeywords{深度学习，自增长，图片验证码，爬虫，大数据}
\begin{cnabstract}

验证码（CAPTCHA）是“Completely Automated Public Tests to tell Computers and Humans Apart”的缩写。其主要思想是通过电脑向用户提问，通过回答来区分人和机器。目前验证码系统分为3种：文本验证码系统，声音验证码系统，图片验证码系统。图片验证码系统以其优良的可用性，安全性，用户友好性逐渐代替了其他系统；然而图片验证码系统也存在致命的缺点：图片需要人工导入。本文提出了一种基于深度学习的自增长图片验证码算法来解决这个问题，它能利用人类验证过程中的输入信息，实现图片数据库的自增长。本算法在解决上述问题的同时，还能大量的带有标签的图片，可以推动其他领域发展（如：搜索引擎的图片语义化搜索，人工智能算法学习库）。\par


本文主要工作有:\par

1.创新性的提出自增长图片验证码系统这一概念。自增长图片验证码系统灵感来源于reCAPTCHA系统，通过对reCAPTCHA思想的改进，使其可以用在图片验证码系统上。\par
2.使用深度学习方法实现自增长图片验证码系统。图片验证码系统最为关键的步骤是图片分割和图像预识别，在这一方面深度卷积神经网络性能优秀，本文使用DeepLearn4J来实现深度卷积神经网络。\par
3.设计并实现超高并发web服务。为了提高系统自增长速率，需要大量用户使用此系统。因而需要将本系统做成web服务，提供给数以万计的网站调用。这就会必然涉及到超高并发，海量数据，授权等问题。本文提出了一整套的解决方案，并在设计时充分考虑到了这些问题。\par
4.通过用户实验测试算法性能。本文对整体设计进行可用性和安全性评估，实现了一个简单的例子并发起一个150人参加的用户实验。实验主要考察自增长图片验证码的用户解决时间，精确度，自增长性能，系统娱乐性和易用性4个方面。
结果显示自增长的图片验证码系统拥有和文本验证码相近的用户解决时间和精确度，在这点上远超其他图片验证码系统；
在系统娱乐性和易用性方面和其他图片验证码系统相近，远超图片验证码系统。除此之外，它还有不错的自增长性能。\par



\setcounter{page}{1}
\end{cnabstract} 

\enkeywords{Deep Learning, Automatic Increase, Image-based CPATCHA, Crawler, Big Data}
\begin{enabstract}
CAPTCHA is short for Completely Automated Public Tests to tell Computers and Humans Apart. The main idea is to distinguish human from computer by asking user questions and analyzing the answers. There are three kinds of CAPTCHA systems now: text-based CAPTCHA systems, audio-based CAPTCHA systems and image-based CAPTCHA systems. Image CAPTCHA systems have gradually replace others for its outstanding availability, security, user-friendliness. However, there is are fatal flows: people need to import images manually. There propose an auto-increase image CAPTCHA algorithm based on deep-learning to solve the problem. It achieves auto-increase with the data people input when try to validate. Not only can the algorithm solve the problem, but also it can learn the labels for no-label images, which can promote the development of other fields(such as: sematic image search, datasets for artificial intelligence learning algorithm).\par

Main work in this paper is following:\par

1. Propose the concept of auto-increase image CAPTCHA system originally. The inspiration comes from reCAPTCHA system. Improve reCAPTCHA so that it can be used in image CAPTCHA system.\par

2. Implement the system with deep learning algorithm. The key steps of the system are image segmentation and image pre-recognition, on which convolutional neural network has an excellent performance. DeepLearn4J is used to implement convolutional neural network.\par

3. Design and implement web service with ultra-high concurrent. In order to improve the growth rate, it requires a large number of users to use, that's also why the system is made a web service to allow millions of people to use it. So, this results in problems about ultra-high concurrent ,mass data, authorization and so on. A set of solutions was presented in this paper, and full account was taken when designing.\par

4. Test algorithm performance with user experiments. In this paper, usability and security were assessed. A simple demonstration was achieved, in which 150 people took part. The experiments mainly assess users' choosing time, accuracy, performance of auto-increase, entertainment and ease of use. The results show that users' choosing time and accuracy for image CAPTCHA system are similar with text CAPTCHA system, and are far better than other image CAPTCHA system. Entertainment and ease of use is similar with other image CAPTCHA systems, and far better than text CAPTCHA systems. Besides, it has a good auto-increase performance.\par


\end{enabstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------文章目录-------------
\tableofcontents
\listoffigures
%\addcontentsline{toc}{section}{插图清单}
\listoftables
%\addcontentsline{toc}{section}{附表清单}


%------------------------------------词汇------------------------------------------------------------
\begin{denotation}{2.5}{0}


\item[问题] 验证码系统通过向用户提问来区分人和机器，本文中特指验证码系统提问内容。
\item[主体] 一张图片中可能包含多个物体，本文中将图片中的单个物体称为主体。$x$

\item[Q] 某次生成\emph{问题}的图片集合。

\item[Qu] 生成问题中非确信\emph{主体}集合。
\item[Qc] 生成问题中确信\emph{主体}集合。

\item[I] 数据库中所有\emph{主体}的集合。
\item[Iu] 是一个集合，表示非确信\emph{主体}集。
\item[Ic] 是一个集合，表示确信\emph{主体}集。

\item[N] 数据库中所有\emph{主体}名称的集合。
\item[Nu] 是一个集合，数据库中所有非确信\emph{主体}名称的集合
\item[Nc] 是一个集合，数据库中所有确信\emph{主体}名称的集合


\end{denotation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{arabic}

$body$

%\include{chapters/summery}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%\include{chapters/appendix}  %%附录

\end{document}
